\thetitle

### 2013-04-13 tfpie/tfpie.tex
fixes for formatting

\begin{figure}
\begin{minipage}{3.5in}
\begin{verbatim}

;; A Tree is one of:
;; - (make-leaf Number)
;; - (make-node Tree Number Tree)
(define-struct leaf (v))
(define-struct node (left v right))

@@

(check-expect (sum (make-leaf 7)) 7)
(check-expect 
  (sum (make-node
         (make-leaf 1)
         5 
         (make-node (make-leaf 0)
                    10
                    (make-leaf 0))))
  16)
\end{verbatim}
\end{minipage}
\begin{minipage}{3in}
\begin{verbatim}
#lang class/1
;; A Tree is one of:
;; - (new leaf% Number)
;; - (new node% Tree Number Tree)
;; and implements
;; sum : -> Number
;; sums the elements of this tree

@@

(check-expect (sum (new leaf% 7)) 7)
(check-expect 
  (sum (new node%
         (new leaf% 1)
         5 
         (new node% (new leaf% 0) 
                    10
                    (new leaf% 0))))
  16)
\end{verbatim}
\end{minipage}
\caption{Binary tree sum in the first course, and in our approach}
\end{figure}

In Java:

>>>>

\begin{figure}
\begin{minipage}[t]{3.5in}
\begin{verbatim}
#lang bsl
;; A Tree is one of:
;; - (make-leaf Number)
;; - (make-node Tree Number Tree)
(define-struct leaf (v))
(define-struct node (left v right))

@@

(check-expect (sum (make-leaf 7)) 7)
(check-expect 
  (sum (make-node
         (make-leaf 1)
         5 
         (make-node (make-leaf 0)
                    10
                    (make-leaf 0))))
  16)
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{3in}
\begin{verbatim}
#lang class/1
;; A Tree is one of:
;; - (new leaf% Number)
;; - (new node% Tree Number Tree)
;; and implements
;; sum : -> Number
;; sums the elements of this tree

@@

(check-expect (sum (new leaf% 7)) 7)
(check-expect 
  (sum (new node%
         (new leaf% 1)
         5 
         (new node% (new leaf% 0) 
                    10
                    (new leaf% 0))))
  16)
\end{verbatim}
\end{minipage}
\caption{Binary tree sum in Beginning Student and in our language}
\end{figure}
